MSB104_assignment1

### 2023-10-04 MSB104_assignment1.qmd
Updated download population 04.10.23

```{r}
#| label: Datasets
#| echo: false
library(readr)
nama_10r_3gdp <- read_delim("nama_10r_3gdp.tsv", 
    delim = "\t", escape_double = FALSE, 
    na = "NA", trim_ws = TRUE, 
    show_col_types = FALSE)

demo_r_pjanaggr3 <- read_delim("demo_r_pjanaggr3.tsv", 
    delim = "\t", escape_double = FALSE, 
    na = "NA", trim_ws = TRUE,
    show_col_types = FALSE)
```

```{r}
gdp <- nama_10r_3gdp
```

```{r}
str(gdp)
```

```{r}
countries_to_keep <- c("FI", "DE", "RO")
filtered_data <- gdp %>%
  filter(substr(`unit,geo\\time`, 9, 10) %in% countries_to_keep)
selected_columns <- filtered_data %>%
  select(`unit,geo\\time`, `2000`:`2020`)
```

```{r}
gdp_DE_FI_RO <- selected_columns 
```

>>>>

```{r}
library(readr)
demo_r_pjanaggr3_page_linear_csv <- read_csv("demo_r_pjanaggr3_page_linear.csv.gz", 
    na = "NA", show_col_types = FALSE)
```

```{r}
DE_FI_RO_pop <- demo_r_pjanaggr3_page_linear_csv |>
	filter(str_sub
	       (geo, start = 1L, end = 2L) %in% c("DE", "FI", "RO")) |>
	select(year = TIME_PERIOD, geo, pop = OBS_VALUE)
```
